Composable Generalized Consensus

### 2015-06-03 paper/paper.tex
Fixed little errors in paper.tex

In fast CGC round, abort and learn quorums are defined such that
the intersection between any two learn quorums is nonempty and the
intersection between any two learn quorums and an abort quorum is
nonempty.  The definition leads to three interesting cases: $LearnQ =
AbortQ = Q\left( 2/3 \right)$; $LearnQ = Q\left( 1/2 \right)$ and
$AbortQ = Q\left( 3/4 \right)$; $LearnQ = \aset{Acceptors}$ and
$AbortQ = \aset{\aset{a : a \in Acceptors}}$.
The operator $SafeAborts\left( R \right)$ is defined as the set of
maximal elements over the set 
\begin{equation}
\aset{GLB\left( \aset{hist\left[ a
\right] : a \in R \cap L \wedge hist\left[ a \right]\neq None} \right)
: L \in LearnQ}.
\end{equation}

>>>>

In fast CGC round, abort and learn quorums are defined such that
the intersection between any two learn quorums is nonempty and the
intersection between any two learn quorums and an abort quorum is
nonempty.  The definition leads to three interesting cases: $LearnQ =
AbortQ = Q\left( 2/3 \right)$; $LearnQ = Q\left( 1/2 \right)$ and
$AbortQ = Q\left( 3/4 \right)$; $LearnQ = \aset{Acceptors}$ and
$AbortQ = Q\left( 0 \right)$.
The operator $SafeAborts\left( R \right)$ is defined as the set of
maximal elements over the set 
\begin{equation}
\aset{GLB\left( \aset{hist\left[ a
\right] : a \in R \cap L \wedge hist\left[ a \right]\neq None} \right)
: L \in LearnQ}.
\end{equation}
